Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-10 paper.tex
Story module citations.

XXX stories consist of elements.  all elements contain preconditions,
and actions.  cite PLANNER.

In principle, all rules for all elements of all stories are evaluated
continuously to determine the actions of the narrative agents.  This
is made computationally efficient using the Rete
algorithm~\cite{rete}.  The Rete algorithm requires that our
conditions are in Normal Form\footnote{BE PRECISE HERE}, but actions
can be arbitrarily complex.

@@

Story modules can be inherited and extended, as figure~\ref{fig:rules2}
shows.  This makes it easy to take an existing story and modify it to
better suit particular interests or a particular type of learner, or
just to add variety.  This can lead to conflicts: multiple versions of
a story, or multiple variant elements within a story, may have their
preconditions satisfied simultaneously.

>>>>

Stories consist of a sequence of \textit{scenes}, in addition to
characters, locations, and activity information.  Scenes are ``goals''
in the STRIPS formalism~\cite{strips}, and consist of
action descriptions, preconditions, and effects.
In principle, all preconditions for all scenes of all story modules
are evaluated continuously to determine the actions of the narrative
agents.  This is made computationally efficient using the Rete
algorithm.  Dialog is expressed using Curveship-style
templates~\cite{montfort:curveship}.

%  The Rete algorithm requires that our conditions are in Normal
%  Form\footnote{BE PRECISE HERE}, but actions can be arbitrarily complex.

@@

Story modules can be inherited and extended, as shown in the figure.
This makes it easy to take an existing story and modify it to
better suit particular interests or a particular type of learner, or
just to add variety.  This can lead to conflicts: multiple versions of
a story, or multiple variant elements within a story, may have their
preconditions satisfied simultaneously.
